Discovering governing reactions from concentration data

### 2018-01-29 docs/manuscript.tex

	\section{Examples}

@@

	In each of the considered examples the library of ansatz reactions $\Theta$ contains
	\begin{colbox}{F8E0E0}
		introduce ansatz functions
	\end{colbox}

@@

>>>>

	\section{Examples}\label{sec:examples}

@@

	In each of the considered examples the library $\Theta$ includes, among others, the reactions of the example system described in Section \ref{sec:generegulation}. The full set of reactions can be found in the Appendix, Table \ref{tab:reaction-library}.

@@

	\section{Appendix}
	\begin{table}
		\centering
		\begin{tabular}{rclcc}
			\multicolumn{3}{c}{Reaction} & rate & description \\ \hline\noalign{\vskip .1cm}
			$\ce{DNA_A}$ &$\ce{->}$& $\ce{DNA_A + mRNA_A }$ & $k_1 = 1.8$ & transcription of $\ce{mRNA_A}$\\
			$\ce{mRNA_A}$ &$\ce{->}$& $\ce{mRNA_A + A}$ & $k_2 = 2.1$ & translation of $\ce{A}$ proteins\\
			$\ce{mRNA_A}$ &$\ce{->}$& $\ce{\emptyset}$ & $k_3 = 1.3$ & $\ce{mRNA_A}$ decay\\
			$\ce{A}$ &$\ce{->}$& $\ce{\emptyset }$ & $k_4 = 1.5$ & decay of $\ce{A}$ proteins\\
			$\ce{DNA_B}$ &$\ce{->}$& $\ce{DNA_B + mRNA_B }$ & $k_5 = 2.2$ & transcription of $\ce{mRNA_B}$\\
			$\ce{mRNA_B}$ &$\ce{->}$& $\ce{mRNA_B + B}$ & $k_6 = 2.0$ & translation of $\ce{B}$ proteins\\
			$\ce{mRNA_B}$ &$\ce{->}$& $\ce{\emptyset }$ & $k_7 = 2.0$ & $\ce{mRNA_B}$ decay\\
			$\ce{B}$ &$\ce{->}$& $\ce{\emptyset }$ & $k_8 = 2.5$ & decay of $\ce{B}$ proteins\\
			$\ce{DNA_C}$ &$\ce{->}$& $\ce{DNA_C + mRNA_C }$ & $k_9 = 3.2$ & transcription of $\ce{mRNA_C}$\\
			$\ce{mRNA_C}$ &$\ce{->}$& $\ce{mRNA_C + C}$ & $k_{10} = 3.0$ & translation of $\ce{C}$ proteins\\
			$\ce{mRNA_C}$ &$\ce{->}$& $\ce{\emptyset }$ & $k_{11} = 2.3$ & $\ce{mRNA_C}$ decay\\
			$\ce{C}$ &$\ce{->}$& $\ce{\emptyset }$ & $k_{12} = 2.5$ & decay of $\ce{C}$ proteins\\
			$\ce{mRNA_A + A}$ &$\ce{->}$& $A$ & $k_{13} = 0$ & self regulation of $\ce{A}$ proteins\\
			$\ce{mRNA_B + B}$ &$\ce{->}$& $B$ & $k_{14} = 0$ & self regulation of $\ce{B}$ proteins\\
			$\ce{mRNA_C + C}$ &$\ce{->}$& $C$ & $k_{15} = 0$ & self regulation of $\ce{C}$ proteins\\
			$\ce{mRNA_B + A}$ &$\ce{->}$& $A$ & $k_{16} = 0$ & cyclic regulation of $\ce{A}$ proteins\\
			$\ce{mRNA_C + B}$ &$\ce{->}$& $B$ & $k_{17} = 0$ & cyclic regulation of $\ce{B}$ proteins\\
			$\ce{mRNA_A + C}$ &$\ce{->}$& $C$ & $k_{18} = 0$ & cyclic regulation of $\ce{C}$ proteins\\
			$\ce{mRNA_C + A}$ &$\ce{->}$& $A$ & $k_{16} = 6.0$ & cyclic regulation of $\ce{A}$ proteins\\
			$\ce{mRNA_B + C}$ &$\ce{->}$& $C$ & $k_{17} = 4.0$ & cyclic regulation of $\ce{C}$ proteins\\
			$\ce{mRNA_A + B}$ &$\ce{->}$& $B$ & $k_{18} = 3.0$ & cyclic regulation of $\ce{B}$ proteins\\
			$\ce{mRNA_A + A}$ &$\ce{->}$& $\ce{mRNA_A}$ & $k_{19} = 0$ & artificial fusion\\
			$\ce{mRNA_B + B}$ &$\ce{->}$& $\ce{mRNA_B}$ & $k_{20} = 0$ & artificial fusion\\
			$\ce{mRNA_C + C}$ &$\ce{->}$& $\ce{mRNA_C}$ & $k_{21} = 0$ & artificial fusion\\
			$\ce{mRNA_A + B}$ &$\ce{->}$& $\ce{mRNA_A}$ & $k_{22} = 0$ & artificial fusion\\
			$\ce{mRNA_B + C}$ &$\ce{->}$& $\ce{mRNA_B}$ & $k_{23} = 0$ & artificial fusion\\
			$\ce{mRNA_C + A}$ &$\ce{->}$& $\ce{mRNA_C}$ & $k_{24} = 0$ & artificial fusion\\
			$\ce{mRNA_A + C}$ &$\ce{->}$& $\ce{mRNA_A}$ & $k_{25} = 0$ & artificial fusion\\
			$\ce{mRNA_B + A}$ &$\ce{->}$& $\ce{mRNA_B}$ & $k_{26} = 0$ & artificial fusion\\
			$\ce{mRNA_C + B}$ &$\ce{->}$& $\ce{mRNA_C}$ & $k_{27} = 0$ & artificial fusion\\
			$\ce{A + A}$ &$\ce{->}$& $\ce{A}$ & $k_{28} = 0$ & $\ce{A}$ regulates $\ce{A}$\\
			$\ce{B + B}$ &$\ce{->}$& $\ce{B}$ & $k_{29} = 0$ & $\ce{B}$ regulates $\ce{B}$\\
			$\ce{C + C}$ &$\ce{->}$& $\ce{C}$ & $k_{30} = 0$ & $\ce{C}$ regulates $\ce{C}$\\
			$\ce{B + A}$ &$\ce{->}$& $\ce{A}$ & $k_{31} = 0$ & artificial fusion between proteins\\
			$\ce{C + B}$ &$\ce{->}$& $\ce{B}$ & $k_{32} = 0$ & artificial fusion between proteins\\
			$\ce{A + C}$ &$\ce{->}$& $\ce{C}$ & $k_{33} = 0$ & artificial fusion between proteins\\
			$\ce{C + A}$ &$\ce{->}$& $\ce{A}$ & $k_{34} = 0$ & artificial fusion between proteins\\
			$\ce{B + C}$ &$\ce{->}$& $\ce{C}$ & $k_{35} = 0$ & artificial fusion between proteins\\
			$\ce{A + B}$ &$\ce{->}$& $\ce{B}$ & $k_{36} = 0$ & artificial fusion between proteins\\
			$\ce{A}$ &$\ce{->}$& $\ce{B}$ & $k_{37} = 0$ & artificial conversion between proteins\\
			$\ce{B}$ &$\ce{->}$& $\ce{C}$ & $k_{38} = 0$ & artificial conversion between proteins\\
			$\ce{C}$ &$\ce{->}$& $\ce{A}$ & $k_{39} = 0$ & artificial conversion between proteins\\
			$\ce{A}$ &$\ce{->}$& $\ce{C}$ & $k_{40} = 0$ & artificial conversion between proteins\\
			$\ce{C}$ &$\ce{->}$& $\ce{B}$ & $k_{41} = 0$ & artificial conversion between proteins\\
			$\ce{B}$ &$\ce{->}$& $\ce{A}$ & $k_{42} = 0$ & artificial conversion between proteins
		\end{tabular}
		\caption{Full set of ansatz reactions $\Theta$ used in Section \ref{sec:examples}.}
		\label{tab:reaction-library}
	\end{table}
